A finite-state morphological transducer for Kyrgyz

### 2011-10-24 dev/paper/abstract.tex
more cleaing up

%\subsection{Number of stems}
Table~\ref{table:stems} gives the approximate number of stems in each main word class. The numbers are approximate as some words may have two entries for one stem (for example if a set of forms is irregular).

\begin{table*}
	\centering
	\begin{tabular}{lr}
		\toprule
		Part of speech & Number of stems\\
		\midrule
		Noun & 4,731\\
		Adjective & 924\\
		Verb & 896 \\
		Proper noun & 745\\
		Adverb & 213\\
		Numeral & 50\\
		Postposition & 42\\
		Conjunction & 36\\
		Pronoun & 29\\
		Determiner & 27\\
		\midrule
		Total:     & 7,333\\
		\bottomrule
	\end{tabular}
	\caption{FIXME}\label{table:stems}
	%FIXME: are we putting captions above or below tables?  I like them better below, but I got the impression that there's some standard to have them above.  Maybe it was just UW being table Nazis for my MA thesis.
\end{table*}

%\subsection{Coverage}

%FIXME: is this about right?  and I mean all aspects of the paragraph
%FIXME: ZZ needs to be replaced with .. ?
To calculate the naïve coverage\footnote{FIXME} of the analyser, two corpora were used, the first was a database dump of the Kyrgyz Wikipedia, dated 2011-09-23. The second was a corpus generated from the archives of Radio Free Europe / Radio Liberty's Kyrgyz service, \href{http://www.azattyk.org}{azattyk.org}.  The RFERL corpus was built using a script that scraped the archives for all articles from 2010, which include articles on a wide variety of topics, from sports to politics and from culture to current events.

>>>>

The analyser contains a total of 7333 stems.  To calculate the coverage of the analyser, two corpora were used, the first was a database dump of the Kyrgyz Wikipedia, dated 2011-09-23. The second was a corpus generated from the archives of Radio Free Europe / Radio Liberty's Kyrgyz service, \href{http://www.azattyk.org}{azattyk.org}.  The RFERL corpus was built using a script that scraped the archives for all articles from 2010, which include articles on a wide variety of topics, from sports to politics and from culture to current events.
